Psychophysics of musical elements in the discrete-time representation of sound

### 2013-10-02 article/article.tex
arrumadas figuras anteriores que estavam pequenas e arrumado texto ateh os ruidos individuais

\begin{figure}[h!]
    \centering
        \includegraphics[width=\columnwidth]{figures/lut}
    \caption{Search in the \emph{lookup table} to synthesize sounds in different frequencies using an unique waveform with high resolution.}
        \label{fig:lut}                                                                                                            
\end{figure}

@@

\begin{figure}[h!]
     \centering
         \includegraphics[width=\columnwidth]{figures/convolucao}
     \caption{Graphical interpretation of convolution. Each resulting sample is the sum of the previous samples of a signal, with each one multiplied by the retrograde of the other sequence.}
         \label{fig:conv}
\end{figure}

@@

\begin{figure}[h!]
    \centering
        \includegraphics[width=\columnwidth]{figures/delays}
    \caption{Convolution with the impulse: shifting (a), delay lines (b) and granular synthesis~(c). Disposed in increasing order of its pulse density.}
        \label{fig:delays}
\end{figure}

@@

\begin{figure}[h!]
    \centering
        \includegraphics[width=\columnwidth]{figures/iir}
    \caption{Modules for the frequency response (a), (b), (c) and (d) for IIR filters of equations~\ref{eq:passa-baixas}, \ref{eq:passa-altas}, \ref{eq:passa-banda} and \ref{eq:rejeita-banda} respectively, considering different cutoff frequencies, center frequencies and band width.}
        \label{fig:iir}
\end{figure}

@@

Generally, sounds without a defined pitch are called noise~\cite{Lacerda}.
They are important musical sounds, as noise present in piano notes, violin, etc. Besides that, the majority of percussion instruments do not have precise pitch and their sounds are generally comprehended as noise~\cite{Roederer}. In electronic music, including electro-acoustic and dance genres, noise has diverse uses, and frequently characterizes the music style~\cite{Cook}.

The absence of a defined pitch is due to the absence of a harmonic organization in the sinusoidal components that compose the sound.
In this way, there are many ways to generate noise.
The use of random values to generate the sound sequence $T_i$ is an attractive method but the result is generally not useful because it tends to the white noise~\cite{Cook}.

Another way is to generate noise using the desired spectrum, from which it is possible to perform the inverse Fourier transform.
The spectral distribution should be done with care because, if it uses the same phase or phases with strong correlation, the synthesized sound will include considerably amount of concentrated energy in some periods of its duration.

\begin{figure}[htpq!]
     \centering
         \includegraphics[width=\columnwidth]{figures/ruidos}
     \caption{Colors of noise generated by equations~\ref{eq:branco}, \ref{eq:rosa}, \ref{eq:marrom}, \ref{eq:azul} and \ref{eq:violeta}: resulting spectrum and waveforms.}
         \label{fig:ruidos}
\end{figure}

Some noise with static spectrum are listed below. They are called \emph{colors of noise} since they are associated with colors.
Figure~\ref{fig:ruidos} shows the spectrum profile and the corresponding sound sequence side-by-side. All the noise were generated with a same phase, making it possible to observe the contributions of different regions of the spectrum.

>>>>

\begin{figure*}
    \centering
        \includegraphics[width=\textwidth]{figures/lut}
    \caption{Search in the \emph{lookup table} to synthesize sounds in different frequencies using an unique waveform with high resolution.}
        \label{fig:lut}                                                                                                            
\end{figure*}

@@

\begin{figure*}
     \centering
         \includegraphics[width=\textwidth]{figures/convolucao}
     \caption{Graphical interpretation of convolution. Each resulting sample is the sum of the previous samples of a signal, with each one multiplied by the retrograde of the other sequence.}
         \label{fig:conv}
\end{figure*}

@@

\begin{figure*}
    \centering
        \includegraphics[width=\textwidth]{figures/delays}
    \caption{Convolution with the impulse: shifting (a), delay lines (b) and granular synthesis~(c). Disposed in increasing order of its pulse density.}
        \label{fig:delays}
\end{figure*}

@@

\begin{figure*}
    \centering
        \includegraphics[width=\textwidth]{figures/iir}
    \caption{Modules for the frequency response (a), (b), (c) and (d) for IIR filters of equations~\ref{eq:passa-baixas}, \ref{eq:passa-altas}, \ref{eq:passa-banda} and \ref{eq:rejeita-banda} respectively, considering different cutoff frequencies, center frequencies and band width.}
        \label{fig:iir}
\end{figure*}

@@

Generally, sounds without an explicit pitch are called noise~\cite{Lacerda}.
They are important musical sounds, as noise present in piano notes, violin, etc. Besides that, the majority of percussion instruments does not exhibit an unequivocal pitch and their sounds are generally regarded as noise~\cite{Roederer}. In electronic music, including electro-acoustic and dance genres, noise has diverse uses and frequently characterizes the music style~\cite{Cook}.

The absence of a definite pitch is due to the lack of a perceptible harmonic organization in the sinusoidal components of the sound.
Hence, there are many ways to generate noise.
The use of random values to generate the sound sequence $T_i$ is an attractive method but not outstandingly useful because it tends to produce white noise with little or no variations~\cite{Cook}.

Another way is to generate noise is by using the desired spectrum, from which it is possible to perform the inverse Fourier transform.
The spectral distribution should be done with care: if phases of components present proeminent correlation, the synthesized sound will concentrate energy in some periods of its duration.

\begin{figure*}
     \centering
         \includegraphics[width=\textwidth]{figures/ruidos}
     \caption{Colors of noise generated by equations~\ref{eq:branco}, \ref{eq:rosa}, \ref{eq:marrom}, \ref{eq:azul} and \ref{eq:violeta}: spectrum and waveforms.}
         \label{fig:ruidos}
\end{figure*}

Some noise with static spectrum are listed below. They are called \emph{colored noise} since they are associated with colors.
Figure~\ref{fig:ruidos} shows the spectrum profile and the corresponding sonic sequence side-by-side. All five noises were generated with the same phase for each component, making it possible to observe the contributions of different parts of the spectrum.
